---
title: "Visualisations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{visualisations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fgu.avoidance)
animals <- load_data(file.path("..", "inst", "extdata", "run", "three-animals.csv"))
animal <- animals$animal_8
```


## Plotting animal path during the trial
```{r}
plot_path(animal)
```

If you need to change the background image, you can either pass it your own, or you can use the function `apparatus_image_path` and set the argument `darkside` to be left or right. 

```{r}
plot_path(animal, center = TRUE, background = apparatus_image_path(darkside = "left"))
```

And we can plot without the background image

```{r}
plot_path(animal, background = NULL)
```
## Plotting area presence

```{r}
plot_area_presence(animal, darkside = "right")
```

Or we can flip the left right coloring
```{r}
plot_area_presence(animal, darkside = "left")
```

## Plotting crossings

There is a quick function to plot animal crossings to demonstrate that everything works as intended
```{r}
crosses <- collect_crosses(animal)
plot_crosses(animal, crosses$index, timewindow = 1)
```