---
title: "Cross testing"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "12/01/2020"
output: html_document
---

```{r setup, include=FALSE}
library(fgu.avoidance)
library(dplyr)
filepath <- "../example-data/three-animals.CSV"

obj <- load_data(filepath)
obj <- add_areas(obj)
obj <- obj$animal_14
knitr::opts_chunk$set(echo = FALSE)
```

# Crosses testing

Due to the issues with the software, it is necessary to redefine the number of crosses slightly differently. The main issue is the animal "peeking" out into the zone but not actually visiting it. We then end up with much higher number of crosses than intended. The way to circumwent this is to set a central zone in which the "cross" doesn't count. This is how the Arena then looks

```{r}
plt <- ggplot() + geom_box_room(fill = "grey20", alpha = 0.3) + geom_central_zone(fill = "red", alpha = 0.2) + theme_void()
# Add some text??
plt
```

The zone in the middle is the "noman's zone", where the cross doesn't count as a cross. The animal needs to cross from either of the grey areas to count as a cross.

The following tracks are therefore considered crosses:
```{r}
cross_left_right <- get_area_visits(obj$position, "left", from="right", between_allowed = 1)
cross_right_left <- get_area_visits(obj$position, "right", from="left", between_allowed = 1)
plot_crosses(obj, union(cross_left_right, cross_right_left))
```

Whereas these tracks would not be counted as middle crosses, although they might cross the midline
```{r}
cross_left_central <- get_area_visits(obj$position, "left", from="central", between_allowed = 1)
cross_only_left <- setdiff(cross_left_central, cross_left_right)
cross_right_central <- get_area_visits(obj$position, "right", from="central", between_allowed = 1)
cross_only_right <- setdiff(cross_right_central, cross_right_left)

plot_crosses(obj, union(cross_only_left, cross_only_right))
```